Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-06-30 literature/paper_draft.qmd
Talk about single-level approaches

<!-- ############  Background  ############ -->

@@

  - Heuristic methods
  - Optimal combination methods (OLS, WLS)
  - MinT
  - Bayesian, Machine learning
  - Probabilistic methods

@@

The hierarchical structure can be represented as a tree, as shown in @fig-hierarchy. The top level of the tree represents the total value of all series, while the lower levels represent the series at different levels of disaggregation. When there are attributes of interest that are crossed, such as the Starbucks drinks sales at any aggregation level (brand-wise, national, city, or outlet) is also considered by kinds of drinks (e.g., coffees, refreshers), the structure is described as a grouped time series (illustrated in @fig-grouped).

@@

We refer to $\tilde{\boldsymbol{y}}_{t+h|t}$ as coherent forecasts, as they respect the aggregation structure. We also refer to this way of obtaining coherent forecasts by summing the bottom-level forecasts as the bottom-up approach. However, generating forecasts this way is anchored only to prediction models at a single level, and will not be utilising the information from other levels. This drawback applies to the top-down and middle-out approaches. For example, the bottom-level data can be very noisy or even intermittent, and the higher-level data might be smoother due to the aggregation.

>>>>

<!-- ############  Intro  ############ -->

@@

  - Single level methods
  - Optimal combination methods (OLS, WLS)
  - MinT
  - Bayesian, Machine learning
  - Probabilistic methods

Traditionally, forecasting these hierarchical time series has been done using single-level methods, such as bottom-up, top-down, and middle-out approaches. Bottom-up methods involve generating forecasts for the bottom-level series and aggregating them to higher levels. Top-down methods start with forecasts for the only top level and disaggregate them down. Middle-out methods combine both approaches by forecasting a middle level and then aggregating or disaggregating as needed. Despite their simplicity, these methods only anchor forecasts to a single level, implying a large loss of information on the hierarchy's inherent correlation structure. Furthermore, as we will see in @sec-hierarchy, the disaggregation becomes more complex when structure is grouped since the disaggregation paths are not unique.

<!-- Include more details on the gaps for each of these methods, such as bias, high variance? -->

@@

The hierarchical structure can be represented as a tree, as shown in @fig-hierarchy. The top level of the tree represents the total value of all series, while the lower levels represent the series at different levels of disaggregation. When there are attributes of interest that are crossed, such as the Starbucks drinks sales at any aggregation level (brand-wise, national, city, or outlet) is also considered by kinds of drinks (e.g., coffees, refreshers), the structure is described as a grouped time series. As illustrated in @fig-grouped, the aggregation or disaggregation paths are not unique.

@@

We refer to $\tilde{\boldsymbol{y}}_{t+h|t}$ as coherent forecasts, as they respect the aggregation structure. We also refer to this way of obtaining coherent forecasts by summing the bottom-level forecasts as the bottom-up approach. However, generating forecasts this way is anchored only to prediction models at a single level, and will not be utilising the inherent information from other levels. This drawback applies to the top-down and middle-out approaches. For example, the bottom-level data can be very noisy or even intermittent, and the higher-level data might be smoother due to the aggregation.
